NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-19 results.tex
relative aa contrib

@@

>>>>

In this section we present numerical results for the NLO QCD and NLO EW 
corrections in the production of 
(at least) two 
isolated photons, both inclusively and in association with at least one 
or two jets, $\text{pp}\to \gamma\gamma+0,1,2\,\text{jets}$ at the 
LHC at a centre-of-mass energy of 13\,TeV. 
Our calculation is performed in the Standard Model using the complex-mass 
scheme with the following input parameters
\begin{center}
  \begin{tabular}{rclrcl}
    $\alpha(0)$ &\shortequal& $1/137.03599976$  \qquad &&& \\
    $m_W$ &\shortequal& $80.385\; \text{GeV}$       & $\Gamma_W$ &\shortequal& $2.085\; \text{GeV}$ \\
    $m_Z$ &\shortequal& $91.1876\; \text{GeV}$      & $\Gamma_Z$ &\shortequal& $2.4952\; \text{GeV}$ \\
%     $m_h$ &\shortequal& $125.0\; \text{GeV}$        & $\Gamma_h$ &\shortequal& $0$\\
    $m_t$ &\shortequal& $171.2\; \text{GeV}$        & $\Gamma_t$ &\shortequal& $0$\;.
  \end{tabular}
\end{center}
The width of the top quark can be safely neglected as there are no 
diagrams containing it as an $s$-channel resonance which can potentially 
go on-shell. 
At the same time there are no diagrams 
containing the Higgs boson due to the absence of $W$, $Z$ or top quark 
propagators at LO.
All other parton masses and widths are set to zero, i.e.\ we are working 
in the five-flavour scheme.

@@

\begin{figure}[t!]
  \setlength{\unitlength}{\textwidth}
  \begin{picture}(0,1)
    \put(0,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y1}}
    \put(0,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_y2}}
    \put(0,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/pT_l1l2_comb_log}}
    \put(0.33,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1y2_comb_log}}
    \put(0.33,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y1l1l2_comb_log}}
    \put(0.33,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/m_y2l1l2_comb_log}}
    \put(0.66,0.24){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_y2}}
    \put(0.66,0.12){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y1_l1l2}}
    \put(0.66,0){\includegraphics[width=0.32\textwidth]{figs_aaz_aa-ind/dphi_y2_l1l2}}
  \end{picture}
  \caption{
    Contribution of $\gamma\gamma$-induced production channels at LO.
    \label{fig:aaz:aa-ind}
  }
\end{figure}
